---
title: "Data exploration"
author: "Joan Diaz Calafat"
date: "10/19/2021"
output: html_document
---

Load packages:
```{r}
library(readxl)
library(lubridate)
library(dplyr)
library(ggplot2)
library(plyr)
library(tidyr)
library(reshape2)
library(naniar)
library(zoo)
library(ncdf4)
library(raster)
library(maptools)
#library(GGally)
```

# Load all data:

## Arville:
```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/ARVILLE", 
                        pattern = "*.xlsx", all.files = FALSE, full.names = TRUE, recursive = FALSE,
                        ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

df.list <- lapply(file.list, read_excel)
rm(file.list)
arville.temp <- do.call(rbind, df.list)

oneyear.arville <- seq(ymd_hm('2020-2-1 00:00'),ymd_hm('2021-2-1 00:00'), by = '15 mins')
arville.temp <- arville.temp[which(arville.temp$Date_time %in% oneyear.arville),]

arville.temp$site <- "Arville"
arville.temp$location <- "a"
arville.temp <- separate(arville.temp, Date_time, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

## Hochwald:
```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/HOCHWALD/", 
                        pattern = "*.xlsx", all.files = FALSE, full.names = TRUE, recursive = FALSE,
                        ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

df.list <- lapply(file.list, read_excel)
rm(file.list)
hochwald.temp <- do.call(rbind, df.list)

oneyear.hochwald <- seq(ymd_hm('2020-4-1 00:00'),ymd_hm('2021-4-1 00:00'), by = '15 mins')
hochwald.temp <- hochwald.temp[which(hochwald.temp$Date_time %in% oneyear.hochwald),]

hochwald.temp$site <- "Hochwald"
hochwald.temp <- separate(hochwald.temp, Date_time, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

## Vivarp:
```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/VIVARP/EXCELSUCKS", pattern = "*.csv", all.files = FALSE,
                        full.names = TRUE, recursive = TRUE,
                        ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

df.list <- lapply(file.list, read.csv)
rm(file.list)
vivarp.temp <- do.call(rbind, df.list)

vivarp.temp <- dplyr::rename(vivarp.temp, 
                      "Plot" = "ï..Plot")

vivarp.temp <- na.omit(vivarp.temp)

#Plot 16 used a different logger type that recorded temperatures every 15 min. Let's adjust that to only keeping temperatures at times being o'clock and half-past. Temperature measurements for plot 16 start at quarter-past, and record every 15 min (i.e. XX:15, XX:30, XX:45, XX:00 and so on). Therefore, to keep only temperatures recorded at o'clock and half-past, we'll just keep even rows. 

plot16 <- vivarp.temp[which(vivarp.temp$Plot == 16),]
plot16 <- plot16[seq(0, length(plot16$DateTime), 2),]

#Now remove such plots from the main dataset ( _temp.data_ ) and merge the fixed version with temperatures taken at :00 and :30

vivarp.temp <- vivarp.temp[-which(vivarp.temp$Plot == 16),]
vivarp.temp <- rbind(vivarp.temp, plot16)

rm(plot16)

#Select one year of data
oneyear.vivarp <- seq(from = as.POSIXct("03/07/2020 00:00:00", format = "%d/%m/%Y %H:%M:%S"), to = as.POSIXct("03/07/2021 00:00:00", format = "%d/%m/%Y %H:%M:%S"), by = "30 min")

vivarp.temp$DateTime <- as.POSIXct(vivarp.temp$DateTime, format = "%d/%m/%Y %H:%M:%S")

vivarp.temp <- vivarp.temp[which(vivarp.temp$DateTime %in% oneyear.vivarp),]

vivarp.temp$site <- "Vivarp"
vivarp.temp$location <- "a"
vivarp.temp <- separate(vivarp.temp, DateTime, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

Soil loggers in Vivarp were from a different model. We'll load them separately:

```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/VIVARP/211022 temp data PO_SOIL", pattern = "*.xlsx", all.files = FALSE,
                        full.names = TRUE, recursive = TRUE,
                        ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

df.list <- lapply(file.list, read_excel)
rm(file.list)
vivarp.temp.2 <- do.call(rbind, df.list)

vivarp.temp.2 <- na.omit(vivarp.temp.2)

vivarp.temp.2$Date_time <- as.POSIXct(vivarp.temp.2$Date_time, format = "%d/%m/%Y %H:%M:%S")

oneyear.vivarp.s <- seq(from = as.POSIXct("21/10/2019 00:00:00", format = "%d/%m/%Y %H:%M:%S"), to = as.POSIXct("21/10/2020 00:00:00", format = "%d/%m/%Y %H:%M:%S"), by = "30 min")

vivarp.temp.2 <- vivarp.temp.2[which(vivarp.temp.2$Date_time %in% oneyear.vivarp.s),]

vivarp.temp.2 <- separate(vivarp.temp.2, Date_time, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

Merge both Vivarp temperature objects:

```{r}
vivarp.temp.2$site <- "Vivarp"
vivarp.temp <- rbind(vivarp.temp, vivarp.temp.2)
rm(vivarp.temp.2)
```


## Siljan:
```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/SILJAN/202103_SILJAN_TEMPERATURE", 
                        pattern = "*.xlsx", all.files = FALSE, full.names = TRUE,
                        recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE,                         no.. = FALSE)

df.list <- lapply(file.list, read_excel)
rm(file.list)
siljan.temp <- do.call(rbind, df.list)

oneyear.siljan <- seq(ymd_hm('2019-9-1 00:00'),ymd_hm('2020-9-1 00:00'), by = '15 mins')
siljan.temp <- siljan.temp[which(siljan.temp$Date_time %in% oneyear.siljan),]

siljan.temp$site <- "Siljan"
siljan.temp <- separate(siljan.temp, Date_time, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

## Sandsjö:
```{r}
file.list <- list.files(path = "J:/TEMPERATURE DATA/SANDSJO/Temperature_Vindeln_202010XX", 
                        pattern = "*.xlsx", all.files = FALSE, full.names = TRUE,
                        recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE,
                        no.. = FALSE)

df.list <- lapply(file.list, read_excel)
rm(file.list)
sandsjo.temp <- do.call(rbind, df.list)

oneyear.sandsjo <- seq(ymd_hm('2019-9-2 00:00'),ymd_hm('2020-9-2 00:00'), by = '15 mins')
sandsjo.temp <- sandsjo.temp[which(sandsjo.temp$Date_time %in% oneyear.sandsjo),]

sandsjo.temp$site <- "Sandsjo"
sandsjo.temp <- separate(sandsjo.temp, Date_time, into = c("Date", "time"), sep = " (?=[^ ]+$)")

rm(df.list)
```

# Check data completeness and remove problematic plots

## Arville

```{r}
# In Arville, only air temperature was recorded. But we'll create a new variable (arville.temp.a) just for the sake of nomenclature consistence of this script

arville.temp.a <- arville.temp[which(arville.temp$location == "a"),]
rm(arville.temp)

arville.completeness.a <- dcast(arville.temp.a, Date~Plot, fun.aggregate = mean, value.var = "Temp")

vis_miss(arville.completeness.a, warn_large_data = FALSE)
```

The following plots are problematic (loggers disappeared - all data missing):
3, 17, 26, 32, 33

Let's remove them.

```{r}
arville.temp.a <- arville.temp.a[-which(arville.temp.a$Plot %in% c(3, 17, 26, 32, 33)),]
rm(arville.completeness.a)

arville.temp <- arville.temp.a

rm(arville.temp.a)
```

## Hochwald

```{r}
# Separate soil and air logger data
hochwald.temp.a <- hochwald.temp[which(hochwald.temp$location == "a"),]
hochwald.temp.s <- hochwald.temp[which(hochwald.temp$location == "s"),]
rm(hochwald.temp)

hochwald.completeness.a <- dcast(hochwald.temp.a, Date~Plot, fun.aggregate = mean, value.var = "Temp")
hochwald.completeness.s <- dcast(hochwald.temp.s, Date~Plot, fun.aggregate = mean, value.var = "Temp")

vis_miss(hochwald.completeness.a, warn_large_data = FALSE)
vis_miss(hochwald.completeness.s, warn_large_data = FALSE)
```

The following loggers were problematic and therefore need to be removed:
_Air loggers_:
6 (55.74% of data missing), 34 (63.93% of data missing), 39 (83.06% of data missing)
_Soil loggers_:
29 (100% of data missing)

```{r}
hochwald.temp.a <- hochwald.temp.a[-which(hochwald.temp.a$Plot %in% c(6, 34, 39)),]
hochwald.temp.s <- hochwald.temp.s[-which(hochwald.temp.s$Plot == 29),]

rm(hochwald.completeness.a)
rm(hochwald.completeness.s)

hochwald.temp <- rbind(hochwald.temp.a, hochwald.temp.s)

rm(hochwald.temp.a)
rm(hochwald.temp.s)
```

## Vivarp

```{r}
# Separate soil and air logger data
vivarp.temp.a <- vivarp.temp[which(vivarp.temp$location == "a"),]
vivarp.temp.s <- vivarp.temp[which(vivarp.temp$location == "s"),]
rm(vivarp.temp)

vivarp.completeness.a <- dcast(vivarp.temp.a, Date~Plot, fun.aggregate = mean, value.var = "Temp")
vivarp.completeness.s <- dcast(vivarp.temp.s, Date~Plot, fun.aggregate = mean, value.var = "Temp")

vis_miss(vivarp.completeness.a, warn_large_data = FALSE)
vis_miss(vivarp.completeness.s, warn_large_data = FALSE)
```

The following temperature loggers were problematic and therefore need to be removed:
_Air loggers_:
30 (26.78% of data missing)

_Soil loggers_:
18 (29.97% of data missing), 27 (29.97% of data missing)

```{r}
vivarp.temp.a <- vivarp.temp.a[-which(vivarp.temp.a$Plot == 30),]
vivarp.temp.s <- vivarp.temp.s[-which(vivarp.temp.s$Plot %in% c(18, 27)),]
```

The following data gaps (<10% of logger's data) need to be filled:
Air loggers: 35 (1.64% of data missing)
Soil loggers: 23, 38, 39 (5.45% of data missing in all cases)

We will use the mean of daily mean temperatures for all the loggers in Vivarp when filling these gaps, we will fix these when calculating daily averages.

```{r}
# Get Dates with missing values for plot 35a in Vivarp
missing.vivarp.35a <- vivarp.completeness.a[is.na(vivarp.completeness.a$`35`),]$Date

# Get all the raw data from all loggers but 35 a for these dates
tofill.vivarp.35a <- vivarp.temp.a[which(vivarp.temp.a$Date %in% missing.vivarp.35a),]

# Calculate the mean across all plots per date in the missing dates
filled.vivarp.35a <- aggregate(list(Temp = tofill.vivarp.35a$Temp), by = list(Date = tofill.vivarp.35a$Date), FUN = mean)

# Create extra variables before merging to vivarp.temp.a
filled.vivarp.35a$Plot <- 35
filled.vivarp.35a$time <- NA
filled.vivarp.35a$site <- "Vivarp"
filled.vivarp.35a$location <- "a"

vivarp.temp.a <- rbind(vivarp.temp.a, filled.vivarp.35a)

# Same for 23s

missing.vivarp.23s <- vivarp.completeness.s[is.na(vivarp.completeness.s$`23`),]$Date

tofill.vivarp.23s <- vivarp.temp.s[which(vivarp.temp.s$Date %in% missing.vivarp.23s),]

filled.vivarp.23s <- aggregate(list(Temp = tofill.vivarp.23s$Temp), by = list(Date = tofill.vivarp.23s$Date), FUN = mean)

filled.vivarp.23s$Plot <- 23
filled.vivarp.23s$time <- NA
filled.vivarp.23s$site <- "Vivarp"
filled.vivarp.23s$location <- "s"

vivarp.temp.s <- rbind(vivarp.temp.s, filled.vivarp.23s)

# Same for 38s

missing.vivarp.38s <- vivarp.completeness.s[is.na(vivarp.completeness.s$`38`),]$Date

tofill.vivarp.38s <- vivarp.temp.s[which(vivarp.temp.s$Date %in% missing.vivarp.38s),]

filled.vivarp.38s <- aggregate(list(Temp = tofill.vivarp.38s$Temp), by = list(Date = tofill.vivarp.38s$Date), FUN = mean)

filled.vivarp.38s$Plot <- 38
filled.vivarp.38s$time <- NA
filled.vivarp.38s$site <- "Vivarp"
filled.vivarp.38s$location <- "s"

vivarp.temp.s <- rbind(vivarp.temp.s, filled.vivarp.38s)

# Same for 39s

missing.vivarp.39s <- vivarp.completeness.s[is.na(vivarp.completeness.s$`39`),]$Date

tofill.vivarp.39s <- vivarp.temp.s[which(vivarp.temp.s$Date %in% missing.vivarp.39s),]

filled.vivarp.39s <- aggregate(list(Temp = tofill.vivarp.39s$Temp), by = list(Date = tofill.vivarp.39s$Date), FUN = mean)

filled.vivarp.39s$Plot <- 39
filled.vivarp.39s$time <- NA
filled.vivarp.39s$site <- "Vivarp"
filled.vivarp.39s$location <- "s"

vivarp.temp.s <- rbind(vivarp.temp.s, filled.vivarp.39s)

# Merge everything

vivarp.temp <- rbind(vivarp.temp.a, vivarp.temp.s)

# Clean environment
rm(missing.vivarp.23s)
rm(missing.vivarp.35a)
rm(missing.vivarp.38s)
rm(missing.vivarp.39s)
rm(tofill.vivarp.23s)
rm(tofill.vivarp.35a)
rm(tofill.vivarp.38s)
rm(tofill.vivarp.39s)
rm(filled.vivarp.23s)
rm(filled.vivarp.35a)
rm(filled.vivarp.38s)
rm(filled.vivarp.39s)
rm(vivarp.completeness.a)
rm(vivarp.completeness.s)
rm(vivarp.temp.a)
rm(vivarp.temp.s)
```

## Siljan

```{r}
# Separate soil and air logger data
siljan.temp.a <- siljan.temp[which(siljan.temp$location == "a"),]
siljan.temp.s <- siljan.temp[which(siljan.temp$location == "s"),]
rm(siljan.temp)

siljan.completeness.a <- dcast(siljan.temp.a, Date~Plot, fun.aggregate = mean, value.var = "Temp")
siljan.completeness.s <- dcast(siljan.temp.s, Date~Plot, fun.aggregate = mean, value.var = "Temp")

vis_miss(siljan.completeness.a, warn_large_data = FALSE)
vis_miss(siljan.completeness.s, warn_large_data = FALSE)
```

The following temperature loggers were problematic and therefore need to be removed:
_Air loggers_:
12, 14, 30 (around 97% of data missing)

_Soil loggers_:
2, 13 (97.55% of data missing)

```{r}
siljan.temp.a <- siljan.temp.a[-which(siljan.temp.a$Plot %in% c(12, 14, 30)),]
siljan.temp.s <- siljan.temp.s[-which(siljan.temp.s$Plot %in% c(2, 13)),]

rm(siljan.completeness.a)
rm(siljan.completeness.s)

siljan.temp <- rbind(siljan.temp.a, siljan.temp.s)

rm(siljan.temp.a)
rm(siljan.temp.s)
```


## Sandsjö

```{r}
# Separate soil and air logger data
sandsjo.temp.a <- sandsjo.temp[which(sandsjo.temp$location == "a"),]
sandsjo.temp.s <- sandsjo.temp[which(sandsjo.temp$location == "s"),]
rm(sandsjo.temp)

sandsjo.completeness.a <- dcast(sandsjo.temp.a, Date~Plot, fun.aggregate = mean, value.var = "Temp")
sandsjo.completeness.s <- dcast(sandsjo.temp.s, Date~Plot, fun.aggregate = mean, value.var = "Temp")

vis_miss(sandsjo.completeness.a, warn_large_data = FALSE)
vis_miss(sandsjo.completeness.s, warn_large_data = FALSE)
```

The following temperature loggers were problematic and therefore need to be removed:
_Air loggers_:
37 (83.11% of data missing), 20 (14.17% of data missing)

_Soil loggers_:
31 (23.16% of data missing)

```{r}
sandsjo.temp.a <- sandsjo.temp.a[-which(sandsjo.temp.a$Plot %in% c(20, 37)),]
sandsjo.temp.s <- sandsjo.temp.s[-which(sandsjo.temp.s$Plot == 31),]

rm(sandsjo.completeness.a)
rm(sandsjo.completeness.s)

sandsjo.temp <- rbind(sandsjo.temp.a, sandsjo.temp.s)

rm(sandsjo.temp.a)
rm(sandsjo.temp.s)
```

# Daily temperature variable calculation

Calculate mean values per day and logger before merging:

```{r}
arville.temp <- do.call(data.frame, aggregate(Temp ~  Date + Plot + location + site, data = arville.temp, FUN = function(x) c(mean = mean(x), min = min(x), max = max(x))))

hochwald.temp <- do.call(data.frame, aggregate(Temp ~  Date + Plot + location + site, data = hochwald.temp, FUN = function(x) c(mean = mean(x), min = min(x), max = max(x))))

vivarp.temp <- do.call(data.frame, aggregate(Temp ~  Date + Plot + location + site, data = vivarp.temp, FUN = function(x) c(mean = mean(x), min = min(x), max = max(x))))

siljan.temp <- do.call(data.frame, aggregate(Temp ~  Date + Plot + location + site, data = siljan.temp, FUN = function(x) c(mean = mean(x), min = min(x), max = max(x))))

sandsjo.temp <- do.call(data.frame, aggregate(Temp ~  Date + Plot + location + site, data = sandsjo.temp, FUN = function(x) c(mean = mean(x), min = min(x), max = max(x))))
```


# Vegetation period calculation

First, we need to divide our daily temperatures across a full year in the vegetation period. We understand that the vegetation period starts when the average daily temperature is higher than 5C. For this, we need to pull data from all the loggers as well. As temperature sometimes fluctuates, we will allow up to three days < 5 daily mean before considering the vegetation period over, only if temperature raises above 5C after these days. 

## Arville

*MAYBE WE NEED TO REPEAT THIS ONCE WE GET A WEATHER STATION AND INCLUDE THE CLEAR-CUT LOGGERS IN THE DAILY MEAN AVERAGES!!!*

```{r}
arville.temp.a <- arville.temp[which(arville.temp$location == "a"),]

arville.global.temp.a <- aggregate(list(Temp.mean = arville.temp.a$Temp.mean), by = list(Date = arville.temp.a$Date), FUN = mean)

arville.global.temp.a <- arville.global.temp.a %>% mutate(vegper = rollapply(Temp.mean >= 5, 4, all, align = "left", fill = FALSE))

arville.global.temp.a$Date <- as.POSIXct(arville.global.temp.a$Date)

ggplot(aes(x = Date, y = Temp.mean), data = arville.global.temp.a) + geom_line() + geom_hline(yintercept=5, linetype = "dashed", col = "red") + geom_vline(xintercept = as.POSIXct(as.Date(c("2020-04-03", "2020-11-28"))), linetype="solid", color = "blue", size=0.5)
```

Vegetation period goes from 2020-04-03 to 2020-11-28.

Correct vegetation period variable to get rid of fluctuations in the dataset that includes all plots. Then remove the dataset that averaged everything.

```{r}
veg.per.arville <- seq(from = as.POSIXct("2020-04-03 00:00:00", format = "%Y-%m-%d %H:%M:%S"), to = as.POSIXct("2020-11-28 00:00:00", format = "%Y-%m-%d %H:%M:%S"), by = "1 day")

arville.temp$Date <- as.POSIXct(arville.temp$Date)

arville.temp$vegper <- ifelse(arville.temp$Date %in% veg.per.arville, TRUE,FALSE)

rm(arville.global.temp.a)
rm(arville.temp.a)
```

## Hochwald

```{r}
hochwald.temp.a <- hochwald.temp[which(hochwald.temp$location == "a"),]

hochwald.global.temp.a <- aggregate(list(Temp.mean = hochwald.temp.a$Temp.mean), by = list(Date = hochwald.temp.a$Date), FUN = mean)

hochwald.global.temp.a <- hochwald.global.temp.a %>% mutate(vegper = rollapply(Temp.mean >= 5, 4, all, align = "left", fill = FALSE))

hochwald.global.temp.a$Date <- as.POSIXct(hochwald.global.temp.a$Date)

ggplot(aes(x = Date, y = Temp.mean), data = hochwald.global.temp.a) + geom_line() + geom_hline(yintercept=5, linetype = "dashed", col = "red") + geom_vline(xintercept = as.POSIXct(as.Date(c("2020-04-04", "2020-11-19"))), linetype="solid", color = "blue", size=0.5)
```

Vegetation period goes from 2020-04-04 to 2020-11-19.

Correct vegetation period variable to get rid of fluctuations in the dataset that includes all plots. Then remove the dataset that averaged everything.

```{r}
veg.per.hochwald <- seq(from = as.POSIXct("2020-04-04 00:00:00", format = "%Y-%m-%d %H:%M:%S"), to = as.POSIXct("2020-11-19 00:00:00", format = "%Y-%m-%d %H:%M:%S"), by = "1 day")

hochwald.temp$Date <- as.POSIXct(hochwald.temp$Date)

hochwald.temp$vegper <- ifelse(hochwald.temp$Date %in% veg.per.hochwald, TRUE,FALSE)

rm(hochwald.global.temp.a)
rm(hochwald.temp.a)
```

## Vivarp

```{r}
vivarp.temp.a <- vivarp.temp[which(vivarp.temp$location == "a"),]

vivarp.global.temp.a <- aggregate(list(Temp.mean = vivarp.temp.a$Temp.mean), by = list(Date = vivarp.temp.a$Date), FUN = mean)

vivarp.global.temp.a <- vivarp.global.temp.a %>% mutate(vegper = rollapply(Temp.mean >= 5, 4, all, align = "left", fill = FALSE))

vivarp.global.temp.a$Date <- as.POSIXct(vivarp.global.temp.a$Date)

ggplot(aes(x = Date, y = Temp.mean), data = vivarp.global.temp.a) + geom_line() + geom_hline(yintercept=5, linetype = "dashed", col = "red") + geom_vline(xintercept = as.POSIXct(as.Date(c("2020-11-27", "2021-04-15"))), linetype="solid", color = "blue", size=0.5)
```

In this case is more convenient to calculate the non-vegetation period: 2020-11-27 to 2021-04-15.

Correct vegetation period variable to get rid of fluctuations in the dataset that includes all plots. Then remove the dataset that averaged everything.

```{r}
non.veg.per.vivarp <- seq(from = as.POSIXct("2020-11-27 00:00:00", format = "%Y-%m-%d %H:%M:%S"), to = as.POSIXct("2021-04-15 00:00:00", format = "%Y-%m-%d %H:%M:%S"), by = "1 day")

vivarp.temp$Date <- as.POSIXct(vivarp.temp$Date)

vivarp.temp$vegper <- ifelse(vivarp.temp$Date %in% non.veg.per.vivarp, FALSE,TRUE)

rm(vivarp.global.temp.a)
rm(vivarp.temp.a)
```

*REMEMBER THAT VIVARP USES DIFFERENT TIME PERIODS FOR AIR AND SOIL LOGGERS, AND THEREFORE SOME OF THE DATES IN THE SOIL LOGGESTS (THOSE NOT OVERLAPPING WITH THE AIR LOGGERS) HAVE NOT BEEN CHECKED TO BELONG TO THE VEGETATION PERIOD.*

## Siljan

```{r}
siljan.temp.a <- siljan.temp[which(siljan.temp$location == "a"),]

siljan.global.temp.a <- aggregate(list(Temp.mean = siljan.temp.a$Temp.mean), by = list(Date = siljan.temp.a$Date), FUN = mean)

siljan.global.temp.a <- siljan.global.temp.a %>% mutate(vegper = rollapply(Temp.mean >= 5, 4, all, align = "left", fill = FALSE))

siljan.global.temp.a$Date <- as.POSIXct(siljan.global.temp.a$Date)

ggplot(aes(x = Date, y = Temp.mean), data = siljan.global.temp.a) + geom_line() + geom_hline(yintercept=5, linetype = "dashed", col = "red") + geom_vline(xintercept = as.POSIXct(as.Date(c("2019-10-03", "2020-05-15"))), linetype="solid", color = "blue", size=0.5)
```

The non-vegetation period: 2019-10-03 to 2020-05-15.

Correct vegetation period variable to get rid of fluctuations in the dataset that includes all plots. Then remove the dataset that averaged everything.

```{r}
non.veg.per.siljan <- seq(from = as.POSIXct("2019-10-03 00:00:00", format = "%Y-%m-%d %H:%M:%S"), to = as.POSIXct("2020-05-15 00:00:00", format = "%Y-%m-%d %H:%M:%S"), by = "1 day")

siljan.temp$Date <- as.POSIXct(siljan.temp$Date)

siljan.temp$vegper <- ifelse(siljan.temp$Date %in% non.veg.per.siljan, FALSE,TRUE)

rm(siljan.global.temp.a)
rm(siljan.temp.a)
```

## Sandsjö

```{r}
sandsjo.temp.a <- sandsjo.temp[which(sandsjo.temp$location == "a"),]

sandsjo.global.temp.a <- aggregate(list(Temp.mean = sandsjo.temp.a$Temp.mean), by = list(Date = sandsjo.temp.a$Date), FUN = mean)

sandsjo.global.temp.a <- sandsjo.global.temp.a %>% mutate(vegper = rollapply(Temp.mean >= 5, 4, all, align = "left", fill = FALSE))

sandsjo.global.temp.a$Date <- as.POSIXct(sandsjo.global.temp.a$Date)

ggplot(aes(x = Date, y = Temp.mean), data = sandsjo.global.temp.a) + geom_line() + geom_hline(yintercept=5, linetype = "dashed", col = "red") + geom_vline(xintercept = as.POSIXct(as.Date(c("2019-09-19", "2020-05-20"))), linetype="solid", color = "blue", size=0.5)
```

The non-vegetation period: 2019-09-19 to 2020-05-20.

Correct vegetation period variable to get rid of fluctuations in the dataset that includes all plots. Then remove the dataset that averaged everything.

```{r}
non.veg.per.sandsjo <- seq(from = as.POSIXct("2019-09-19 00:00:00", format = "%Y-%m-%d %H:%M:%S"), to = as.POSIXct("2020-05-20 00:00:00", format = "%Y-%m-%d %H:%M:%S"), by = "1 day")

sandsjo.temp$Date <- as.POSIXct(sandsjo.temp$Date)

sandsjo.temp$vegper <- ifelse(sandsjo.temp$Date %in% non.veg.per.sandsjo, FALSE,TRUE)

rm(sandsjo.global.temp.a)
rm(sandsjo.temp.a)
```

Merge these datasets with all the vegetation periods and divide them creating a dataset for temperatures within the vegetation period and a dataset for the temperatures outide such.

Merge everything:
```{r}
temp.data <- rbind(arville.temp, hochwald.temp, vivarp.temp, siljan.temp, sandsjo.temp)

rm(arville.temp)
rm(hochwald.temp)
rm(vivarp.temp)
rm(siljan.temp)
rm(sandsjo.temp)
```

Export the dataset:

```{r}
write.csv(temp.data, file = "./DATASETS/logger_temp.csv", row.names = FALSE, quote = FALSE)

rm(list = ls())
```
