# Macroclimate data preparation

In this script, we will compile macroclimate data from different sources (ERA5 downloaded directly from the web, ERA5 downloaded through the mcera5 package and weather stations found close to our study sites). We will produce one file as output for each of these sources.

*Code reproducibility*

To allow a better reproducibility of this script, we recommend to use checkpoint() set at 2022-11-21. This allows to install and use the packages that were available and run at the time of making this script.

```{r}
#install.packages("checkpoint")
library(checkpoint)
checkpoint("2022-11-21")
```

Load packages:

```{r, message=FALSE}
library(raster)
library(reshape)
library(reshape2)
library(tidyr)
library(dplyr)
library(lubridate)
library(zoo)
```

# ERA5 from web

First, load the coordinate data of our experimental forests:

```{r}
df <- read.table(file = "./ERA5/coordinates.txt", header = T)

# And keep only lat and lon columns:
coordinates <- data.frame(xcoords = df$lon, ycoords = df$lat)
```

Load climatic ERA5 model: Data source: <https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-land?tab=overview> and <https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-single-levels?tab=form>

```{r}
air.temp.nc <- brick("./ERA5/ERA5_mean.nc")
soil.temp.nc <- brick("./ERA5/ERA5_maxmin.nc", varname = "stl1")
wind.nc <- brick("./ERA5/ERA5_wind.nc")
snow.nc <- brick("./ERA5/ERA5_snowprec.nc", varname = "sd")
prec.nc <- brick("./ERA5/ERA5_snowprec.nc", varname = "tp")
```

And subset the ERA5 data to our climatic extent (earliest date: 2020-01-01; latest date: 2021-07-31).

```{r}
air.temp.nc <- air.temp.nc[[which(getZ(air.temp.nc) >= as.Date("2020-01-01") & getZ(air.temp.nc) <= as.Date("2021-07-31"))]]

soil.temp.nc <- soil.temp.nc[[which(getZ(soil.temp.nc) >= as.Date("2020-01-01") & getZ(soil.temp.nc) <= as.Date("2021-07-31"))]]

wind.nc <- wind.nc[[which(getZ(wind.nc) >= as.Date("2020-01-01") & getZ(wind.nc) <= as.Date("2021-07-31"))]]

snow.nc <- snow.nc[[which(getZ(snow.nc) >= as.Date("2020-01-01") & getZ(snow.nc) <= as.Date("2021-07-31"))]]

prec.nc <- prec.nc[[which(getZ(prec.nc) >= as.Date("2020-01-01") & getZ(prec.nc) <= as.Date("2021-07-31"))]]
```

Convert coordinates to spatial points:

```{r}
coordinates <- SpatialPoints(coords = coordinates, proj4string = crs(air.temp.nc))
```

Extract data from experimental forest coordinates:

```{r}
era5.air.temp <- data.frame(raster::extract(air.temp.nc, coordinates))

era5.soil.temp <- data.frame(raster::extract(soil.temp.nc, coordinates))

wind <- data.frame(raster::extract(wind.nc, coordinates))

snow <- data.frame(raster::extract(snow.nc, coordinates))

prec <- data.frame(raster::extract(prec.nc, coordinates))

rm(air.temp.nc)
rm(soil.temp.nc)
rm(wind.nc)
rm(snow.nc)
rm(prec.nc)
rm(coordinates)
```

Format macroclimate data base:

```{r}
#detach(package:reshape)

rownames(era5.air.temp) <- df$Plot
era5.air.temp <- data.frame(t(era5.air.temp))
era5.air.temp$hour <- rownames(era5.air.temp)
era5.air.temp$hour <- substr(era5.air.temp$hour, 2,11)
era5.air.temp <- melt(era5.air.temp, variable.name = "site", value.name = "era5_meanair")
names(era5.air.temp) <- c("date", "site", "air_temp")
era5.air.temp$air_temp <- era5.air.temp$air_temp-273.15 # Kelvin to celsius

rownames(era5.soil.temp) <- df$Plot
era5.soil.temp <- data.frame(t(era5.soil.temp))
era5.soil.temp$hour <- rownames(era5.soil.temp)
era5.soil.temp$hour <- substr(era5.soil.temp$hour, 2,11)
era5.soil.temp <- melt(era5.soil.temp, variable.name = "site", value.name = "era5_meansoil")
names(era5.soil.temp) <- c("date", "site", "soil_temp")
era5.soil.temp$soil_temp <- era5.soil.temp$soil_temp-273.15 # Kelvin to celsius

rownames(wind) <- df$Plot
wind <- data.frame(t(wind))
wind$hour <- rownames(wind)
wind$hour <- substr(wind$hour, 2,11)
wind <- melt(wind, variable.name = "site", value.name = "era5_wind")
names(wind) <- c("date", "site", "wind")

rownames(snow) <- df$Plot
snow <- data.frame(t(snow))
snow$hour <- rownames(snow)
snow$hour <- substr(snow$hour, 2,11)
snow <- melt(snow, variable.name = "site", value.name = "era5_snow")
names(snow) <- c("date", "site", "snow")

rownames(prec) <- df$Plot
prec <- data.frame(t(prec))
prec$hour <- rownames(prec)
prec$hour <- substr(prec$hour, 2,11)
prec <- melt(prec, variable.name = "site", value.name = "era5_prec")
names(prec) <- c("date", "site", "prec")

rm(df)
```

Temperature data in ERA5 has been downloaded at an hourly basis. Before merging all ERA5 temperatures, we want to aggregate them by date, and differently depending on the temperature variable (i.e. calculate the mean for the average daily temperature, but the min for all the min values recorded by day for the minimum daily temperature). We will also rename the "hour" variable to "Date".

```{r}
era5.meanair.temp <- aggregate(list(era5_meanair = era5.air.temp$air_temp), by = list(Date = era5.air.temp$date, site = era5.air.temp$site), FUN = mean)

era5.maxair.temp <- aggregate(list(era5_maxair = era5.air.temp$air_temp), by = list(Date = era5.air.temp$date, site = era5.air.temp$site), FUN = max)

era5.minair.temp <- aggregate(list(era5_minair = era5.air.temp$air_temp), by = list(Date = era5.air.temp$date, site = era5.air.temp$site), FUN = min)

era5.soil.temp <- aggregate(list(era5_meansoil = era5.soil.temp$soil_temp), by = list(Date = era5.soil.temp$date, site = era5.soil.temp$site), FUN = mean)

era5.soil.temp$Date <- gsub(".", "-", era5.soil.temp$Date, fixed = TRUE)

wind <- aggregate(list(era5_wind = wind$wind), by = list(Date = wind$date, site = wind$site), FUN = max)

wind$Date <- gsub(".", "-", wind$Date, fixed = TRUE)

snow <- aggregate(list(era5_snow = snow$snow), by = list(Date = snow$date, site = snow$site), FUN = mean)

snow$Date <- gsub(".", "-", snow$Date, fixed = TRUE)

prec <- aggregate(list(era5_prec = prec$prec), by = list(Date = prec$date, site = prec$site), FUN = sum)

prec$Date <- gsub(".", "-", prec$Date, fixed = TRUE)
```

And now we can merge such data:

```{r}
era5.temp <- merge_recurse(list(era5.meanair.temp, era5.maxair.temp, era5.minair.temp, era5.soil.temp, wind, snow, prec))
```

Turn "Date" into POSIXct class.

```{r}
era5.temp$Date <- as.POSIXct(era5.temp$Date, format = "%Y-%m-%d")
```

Calculate rolling mean temperature and precipitation for each previous 5 days:

```{r}
era5.temp <- era5.temp %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(era5_prev_av_prec = lag(zoo::rollmean(era5_prec, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>% 
  dplyr::ungroup()

era5.temp <- era5.temp %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(era5_prev_av_temp = lag(zoo::rollmean(era5_meanair, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>% 
  dplyr::ungroup()
```

Export the dataset:

```{r}
write.csv(era5.temp, file = "./DATASETS/ERA5_temp.csv", row.names = FALSE, quote = FALSE)

rm(list = ls())
```

# 'mcera5' package

Install *mcera5* package:

```{r}
remotes::install_github("dklinges9/mcera5")

library(mcera5)
```

set UID and API key:

```{r}
uid <- "..."
cds_api_key <- "..."
```

Use `ecmwfr` package to register your machine with your credentials:

```{r}
ecmwfr::wf_set_key(user = uid,key = cds_api_key,service = "cds")
```

Designate desired bounding coordinates (in WGS84 / EPSG:4326)

```{r}
xmn <- 5
xmx <- 20 
ymn <- 49 
ymx <- 65 
```

Designate a desired temporal extent. We will download years separately and also set the start and ending of each month.

```{r}
# Full period
st_time <-  lubridate::ymd("2019:12:25") # a bit before the real start (01/01/2020) so that we can calculate the 5 day rolling mean
en_time <-  lubridate::ymd("2021:07:31")

# year 2019
st_time2019 <-  lubridate::ymd("2019:12:25") 
en_time2019 <-  lubridate::ymd("2019:12:31")

# year 2020
st_time2020 <-  lubridate::ymd("2020:01:01") 
en_time2020 <-  lubridate::ymd("2020:12:31")

# year 2021
st_time2021 <-  lubridate::ymd("2021:01:01") 
en_time2021 <-  lubridate::ymd("2021:07:31")

# and months separately:

st_jan2020 <-  lubridate::ymd("2020:01:01") 
en_jan2020 <-  lubridate::ymd("2020:01:31")

st_jul2020 <-  lubridate::ymd("2020:06:25") 
en_jul2020 <-  lubridate::ymd("2020:07:31")

st_jan2021 <-  lubridate::ymd("2021:01:01") 
en_jan2021 <-  lubridate::ymd("2021:01:31")

st_jul2021 <-  lubridate::ymd("2021:06:25") 
en_jul2021 <-  lubridate::ymd("2021:07:31")
```

Set a unique prefix for the filename, and the file path for downloaded .nc files

```{r}
file_prefix <- "mcera5" 

file_path <- paste(getwd(),"/mcera5", sep = "")
```

Build requests:

```{r}
req2019 <- build_era5_request(xmin = xmn, xmax = xmx, ymin = ymn, ymax = ymx, start_time = st_time2019, end_time = en_time2019, outfile_name = file_prefix)

req2020 <- build_era5_request(xmin = xmn, xmax = xmx, ymin = ymn, ymax = ymx, start_time = st_time2020, end_time = en_time2020, outfile_name = file_prefix)

req2021 <- build_era5_request(xmin = xmn, xmax = xmx, ymin = ymn, ymax = ymx, start_time = st_time2021, end_time = en_time2021, outfile_name = file_prefix)
```

Submit requests:

```{r}
request_era5(request = req2019, uid = uid, out_path = file_path, overwrite = TRUE) #this can take some time

request_era5(request = req2020, uid = uid, out_path = file_path, overwrite = TRUE) #this can take some time

request_era5(request = req2021, uid = uid, out_path = file_path, overwrite = TRUE) #this can take some time
```

Extract temperature data:

```{r}
my_nc2019 <- paste0(file_path, "/mcera5_2019.nc")
my_nc2020 <- paste0(file_path, "/mcera5_2020.nc")
my_nc2021 <- paste0(file_path, "/mcera5_2021.nc")

df <- read.table(file = "./ERA5/coordinates.txt", header = T)

x <- df$lon
y <- df$lat

# Arville. 
   # Warmest month: July 2020
   # Coldest month: January 2021

arville.warm <- extract_clim(nc = my_nc2020, long =  x[1],  lat   =  y[1], start_time = st_jul2020,  end_time = en_jul2020)

arville.warm$site <- "Arville"

arville.cold <- extract_clim(nc = my_nc2021, long =  x[1],  lat   =  y[1], start_time = st_jan2021,  end_time = en_jan2021)

arville.cold$site <- "Arville"

arville.extra <- extract_clim(nc = my_nc2020, long =  x[1],  lat   =  y[1], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31')) #some extra days for the rolling mean

arville.extra$site <- "Arville"

arville.cold <- rbind(arville.cold, arville.extra) #add the extra days

rm(arville.extra)

# Hochwald
   # Warmest month: July 2020
   # Coldest month: January 2021

hochwald.warm <- extract_clim(nc = my_nc2020, long =  x[2],  lat   =  y[2], start_time = st_jul2020,  end_time = en_jul2020)

hochwald.warm$site <- "Hochwald"

hochwald.cold <- extract_clim(nc = my_nc2021, long =  x[2],  lat   =  y[2], start_time = st_jan2021,  end_time = en_jan2021)

hochwald.cold$site <- "Hochwald"

hochwald.extra <- extract_clim(nc = my_nc2020, long =  x[2],  lat   =  y[2], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31')) #some extra days for the rolling mean

hochwald.extra$site <- "Hochwald"

hochwald.cold <- rbind(hochwald.cold, hochwald.extra) #add the extra days

rm(hochwald.extra)

# Vivarp
   # Warmest month (air): July 2021
   # Coldest month (air): January 2021

vivarp.warm <- extract_clim(nc = my_nc2021, long =  x[3],  lat   =  y[3], start_time = st_jul2021,  end_time = en_jul2021)

vivarp.warm$site <- "Vivarp"

vivarp.cold <- extract_clim(nc = my_nc2021, long =  x[3],  lat   =  y[3], start_time = st_jan2021,  end_time = en_jan2021)

vivarp.cold$site <- "Vivarp"

vivarp.extra <- extract_clim(nc = my_nc2020, long =  x[3],  lat   =  y[3], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31')) #some extra days for the rolling mean

vivarp.extra$site <- "Vivarp"

vivarp.cold <- rbind(vivarp.cold, vivarp.extra) #add the extra days

rm(vivarp.extra)


# Siljan
   # Warmest month: July 2020
   # Coldest month: January 2021

siljan.warm <- extract_clim(nc = my_nc2020, long =  x[4],  lat   =  y[4], start_time = st_jul2020,  end_time = en_jul2020)

siljan.warm$site <- "Siljan"

siljan.cold <- extract_clim(nc = my_nc2021, long =  x[4],  lat   =  y[4], start_time = st_jan2021,  end_time = en_jan2021)

siljan.cold$site <- "Siljan"

siljan.extra <- extract_clim(nc = my_nc2020, long =  x[4],  lat   =  y[4], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31')) #some extra days for the rolling mean

siljan.extra$site <- "Vivarp"

siljan.cold <- rbind(siljan.cold, siljan.extra) #add the extra days

rm(siljan.extra)


# Sandsjö
   # Warmest month: July 2020
   # Coldest month: January 2020

sandsjo.warm <- extract_clim(nc = my_nc2020, long =  x[5],  lat   =  y[5], start_time = st_jul2020,  end_time = en_jul2020)

sandsjo.warm$site <- "Sandsjo"

sandsjo.cold <- extract_clim(nc = my_nc2020, long =  x[5],  lat   =  y[5], start_time = st_jan2020,  end_time = en_jan2020)

sandsjo.cold$site <- "Sandsjo"

sandsjo.extra <- extract_clim(nc = my_nc2019, long =  x[5],  lat   =  y[5], start_time = lubridate::ymd('2019:12:26'),  end_time = lubridate::ymd('2019:12:31')) #some extra days for the rolling mean

sandsjo.extra$site <- "Vivarp"

sandsjo.cold <- rbind(sandsjo.cold, sandsjo.extra) #add the extra days

rm(sandsjo.extra)


# Merge everything:

mcera5 <- rbind(arville.cold, arville.warm, hochwald.cold, hochwald.warm, vivarp.cold, vivarp.warm, siljan.cold, siljan.warm, sandsjo.cold, sandsjo.warm)
```

Calculate daily minimum and maximum temperature from mean values:

```{r}
mcera5 <- dplyr::rename(mcera5,
         "datetime" = "obs_time",
         "mcera5_airtemp" = "temperature")

mcera5$date <- substr(mcera5$datetime, 1,10) # extract dates without time

mcera5_min <- aggregate(list(minair_mcera5 = mcera5$mcera5_airtemp), by = list(site = mcera5$site, Date = mcera5$date), FUN = min)

mcera5_mean <- aggregate(list(meanair_mcera5 = mcera5$mcera5_airtemp), by = list(site = mcera5$site, Date = mcera5$date), FUN = mean)

mcera5_max <- aggregate(list(maxair_mcera5 = mcera5$mcera5_airtemp), by = list(site = mcera5$site, Date = mcera5$date), FUN = max)
```

Extract daily precipitation data:

```{r}
# Arville
arville.warm.prec <-  extract_precip(nc = my_nc2020, long = x[1], lat = y[1], start_time = st_jul2020, end_time = en_jul2020, convert_daily = TRUE)

arville.warm.prec <- data.frame(mcera5_prec = arville.warm.prec, Date = seq(as.Date(st_jul2020), as.Date(en_jul2020), "days"), site = "Arville")

arville.cold.prec <-  extract_precip(nc = my_nc2021, long = x[1], lat = y[1], start_time = st_jan2021, end_time = en_jan2021, convert_daily = TRUE)

arville.cold.prec <- data.frame(mcera5_prec = arville.cold.prec, Date = seq(as.Date(st_jan2021), as.Date(en_jan2021), "days"), site = "Arville")

arville.extra <- extract_precip(nc = my_nc2020, long =  x[1],  lat   =  y[1], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31'), convert_daily = TRUE) #some extra days for the rolling mean

arville.extra <- data.frame(mcera5_prec = arville.extra, Date = seq(as.Date(lubridate::ymd('2020:12:26')), as.Date(lubridate::ymd('2020:12:31')), "days"), site = "Arville")

arville.prec <- rbind(arville.warm.prec, arville.cold.prec, arville.extra)
rm(arville.warm.prec)
rm(arville.cold.prec)
rm(arville.extra)

# Hochwald
hochwald.warm.prec <-  extract_precip(nc = my_nc2020, long = x[2], lat = y[2], start_time = st_jul2020, end_time = en_jul2020, convert_daily = TRUE)

hochwald.warm.prec <- data.frame(mcera5_prec = hochwald.warm.prec, Date = seq(as.Date(st_jul2020), as.Date(en_jul2020), "days"), site = "Hochwald")

hochwald.cold.prec <-  extract_precip(nc = my_nc2021, long = x[2], lat = y[2], start_time = st_jan2021, end_time = en_jan2021, convert_daily = TRUE)

hochwald.cold.prec <- data.frame(mcera5_prec = hochwald.cold.prec, Date = seq(as.Date(st_jan2021), as.Date(en_jan2021), "days"), site = "Hochwald")

hochwald.extra <- extract_precip(nc = my_nc2020, long =  x[2],  lat   =  y[2], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31'), convert_daily = TRUE) #some extra days for the rolling mean

hochwald.extra <- data.frame(mcera5_prec = hochwald.extra, Date = seq(as.Date(lubridate::ymd('2020:12:26')), as.Date(lubridate::ymd('2020:12:31')), "days"), site = "Hochwald")

hochwald.prec <- rbind(hochwald.warm.prec, hochwald.cold.prec, hochwald.extra)
rm(hochwald.warm.prec)
rm(hochwald.cold.prec)
rm(hochwald.extra)

# Vivarp
vivarp.warm.prec <-  extract_precip(nc = my_nc2021, long = x[3], lat = y[3], start_time = st_jul2021, end_time = en_jul2021, convert_daily = TRUE)

vivarp.warm.prec <- data.frame(mcera5_prec = vivarp.warm.prec, Date = seq(as.Date(st_jul2021), as.Date(en_jul2021), "days"), site = "Vivarp")

vivarp.cold.prec <-  extract_precip(nc = my_nc2021, long = x[3], lat = y[3], start_time = st_jan2021, end_time = en_jan2021, convert_daily = TRUE)

vivarp.cold.prec <- data.frame(mcera5_prec = vivarp.cold.prec, Date = seq(as.Date(st_jan2021), as.Date(en_jan2021), "days"), site = "Vivarp")

vivarp.extra <- extract_precip(nc = my_nc2020, long =  x[3],  lat   =  y[3], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31'), convert_daily = TRUE) #some extra days for the rolling mean

vivarp.extra <- data.frame(mcera5_prec = vivarp.extra, Date = seq(as.Date(lubridate::ymd('2020:12:26')), as.Date(lubridate::ymd('2020:12:31')), "days"), site = "Vivarp")

vivarp.prec <- rbind(vivarp.warm.prec, vivarp.cold.prec, vivarp.extra)
rm(vivarp.warm.prec)
rm(vivarp.cold.prec)
rm(vivarp.extra)

# Siljan
siljan.warm.prec <-  extract_precip(nc = my_nc2020, long = x[4], lat = y[4], start_time = st_jul2020, end_time = en_jul2020, convert_daily = TRUE)

siljan.warm.prec <- data.frame(mcera5_prec = siljan.warm.prec, Date = seq(as.Date(st_jul2020), as.Date(en_jul2020), "days"), site = "Siljan")

siljan.cold.prec <-  extract_precip(nc = my_nc2021, long = x[4], lat = y[4], start_time = st_jan2021, end_time = en_jan2021, convert_daily = TRUE)

siljan.cold.prec <- data.frame(mcera5_prec = siljan.cold.prec, Date = seq(as.Date(st_jan2021), as.Date(en_jan2021), "days"), site = "Siljan")

siljan.extra <- extract_precip(nc = my_nc2020, long =  x[4],  lat   =  y[4], start_time = lubridate::ymd('2020:12:26'),  end_time = lubridate::ymd('2020:12:31'), convert_daily = TRUE) #some extra days for the rolling mean

siljan.extra <- data.frame(mcera5_prec = siljan.extra, Date = seq(as.Date(lubridate::ymd('2020:12:26')), as.Date(lubridate::ymd('2020:12:31')), "days"), site = "Siljan")

siljan.prec <- rbind(siljan.warm.prec, siljan.cold.prec, siljan.extra)
rm(siljan.warm.prec)
rm(siljan.cold.prec)
rm(siljan.extra)

# Sandsjö

sandsjo.warm.prec <-  extract_precip(nc = my_nc2020, long = x[5], lat = y[5], start_time = st_jul2020, end_time = en_jul2020, convert_daily = TRUE)

sandsjo.warm.prec <- data.frame(mcera5_prec = sandsjo.warm.prec, Date = seq(as.Date(st_jul2020), as.Date(en_jul2020), "days"), site = "Sandsjo")

sandsjo.cold.prec <-  extract_precip(nc = my_nc2020, long = x[5], lat = y[5], start_time = st_jan2020, end_time = en_jan2020, convert_daily = TRUE)

sandsjo.cold.prec <- data.frame(mcera5_prec = sandsjo.cold.prec, Date = seq(as.Date(st_jan2020), as.Date(en_jan2020), "days"), site = "Sandsjo")

sandsjo.extra <- extract_precip(nc = my_nc2019, long =  x[5],  lat   =  y[5], start_time = lubridate::ymd('2019:12:26'),  end_time = lubridate::ymd('2019:12:31'), convert_daily = TRUE) #some extra days for the rolling mean

sandsjo.extra <- data.frame(mcera5_prec = sandsjo.extra, Date = seq(as.Date(lubridate::ymd('2019:12:26')), as.Date(lubridate::ymd('2019:12:31')), "days"), site = "Sandsjo")


sandsjo.prec <- rbind(sandsjo.warm.prec, sandsjo.cold.prec, sandsjo.extra)
rm(sandsjo.warm.prec)
rm(sandsjo.cold.prec)
rm(sandsjo.extra)
```

Merge precipitation data across al sites:

```{r}
mcera5_prec <- rbind(arville.prec, hochwald.prec, vivarp.prec, siljan.prec, sandsjo.prec)

mcera5_prec$Date <- as.character(mcera5_prec$Date)

rm(arville.prec)
rm(hochwald.prec)
rm(vivarp.prec)
rm(siljan.prec)
rm(sandsjo.prec)
```

Merge all mcera5 datasets:

```{r}
mcera5_merged <- merge(merge(merge(mcera5_min, mcera5_mean, by = c("Date", "site")), mcera5_max, by = c("Date", "site")), mcera5_prec, by = c("Date", "site"))

rm(mcera5_min)
rm(mcera5_max)
rm(mcera5_mean)
rm(mcera5_prec)
```

Calculate rolling mean temperature and precipitation for the previous five days:

```{r}
mcera5_merged <- mcera5_merged %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(mcera5_prev_av_temp = lag(zoo::rollmean(meanair_mcera5, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>%
  dplyr::ungroup()

mcera5_merged <- mcera5_merged %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(mcera5_prev_av_prec = lag(zoo::rollmean(mcera5_prec, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>% 
  dplyr::ungroup()
```

Save the dataset:

```{r}
write.csv(mcera5_merged, file = "./DATASETS/mcera5.csv", quote = FALSE, row.names = FALSE)

# Què feim amb soil data? mcera5 ho descarrega també?

rm(list = ls())
```

# Weather station data

Load data from all weather stations:

```{r}
# Arville_merged

arville.station <- read.csv("./WEATHER STATIONS/Arville_station6476.csv", header = TRUE)

arville.station <- arville.station[which(arville.station$code == 6476),] # we want to keep only the station with code 6476

# Hochwald

hochwald.station <- read.table("./WEATHER STATIONS/Hochwald_station_airtemp.txt", header = TRUE, sep = ";")

# Vivarp

vivarp.station <- read.csv("./WEATHER STATIONS/Vivarp_station.csv", header = TRUE, dec = ".", sep = ";", fileEncoding = "UTF-8-BOM")

# Siljan

siljan.station <- read.table("./WEATHER STATIONS/Siljan_station.txt", header = TRUE, sep = ";", fileEncoding = "UTF-8-BOM")

# Sandsjö

sandsjo.station <- read.table("./WEATHER STATIONS/Sandsjo_station.txt", header = TRUE, sep = ";", fileEncoding = "UTF-8-BOM")
```

We want to keep the following variables: date, time, site, mean air temperature. Let's do that for the weather station data of all sites, using common variable names and calculating daily min, mean and max temperature values.

```{r}
# ARVILLE

# Create site variable
arville.station$site <- "Arville"

# Select variables of interest

arville.station <- separate(arville.station, timestamp, into = c("date", "time"), sep = "T")

arville.station$datetime <- paste(arville.station$date, " ", arville.station$time)
  
arville.station$datetime <- as.POSIXct(arville.station$datetime, format = "%F %T")

arville.station <- arville.station[,which(names(arville.station) %in% c("site", "datetime", "date", "temp", "temp_min", "temp_max"))]

arville.station <- dplyr::rename(arville.station,
                          "station_meanair" = "temp",
                          "station_minair" = "temp_min",
                          "station_maxair" = "temp_max")
                          

arville.dates <- seq(as.Date("2020-06-25"),as.Date("2021-01-31"), by = 'day')

arville.station$date <- substr(arville.station$datetime, 1, 10)

arville.station$date <- as.Date(arville.station$date)

arville.station <- arville.station[which(arville.station$date %in% arville.dates),]

# There is no values for maximum and minimum temperature in all timepoints. We will create our own daily maximum and minimum values from hourly data

arville.station.hourly <- arville.station # backup of hourly data for future graphs

arville.station.minair <- aggregate(list(station_minair = arville.station$station_meanair), by = list(date = arville.station$date), FUN = min)

arville.station.maxair <- aggregate(list(station_maxair = arville.station$station_meanair), by = list(date = arville.station$date), FUN = max)

arville.station.meanair <- aggregate(list(station_meanair = arville.station$station_meanair), by = list(date = arville.station$date), FUN = mean)

# merge

arville.station <- merge_recurse(list(arville.station.minair, arville.station.maxair, arville.station.meanair))

rm(arville.station.maxair)
rm(arville.station.meanair)
rm(arville.station.minair)

arville.station$site <- "Arville"

rm(arville.dates)

#HOCHWALD

# Dates and hours are set together in the same variable with the format YYYYMMDDHH. Let's first split that.

hochwald.station$date <- substr(hochwald.station$MESS_DATUM, 1, 8)

hochwald.station$hour <- substr(hochwald.station$MESS_DATUM, 9, 10)

# Set dates as dates
hochwald.station$date <- as.Date(hochwald.station$date, format = "%Y%m%d")

hochwald.station$datetime <- paste(hochwald.station$date, paste(hochwald.station$hour,":00:00", sep = ""))

hochwald.station$datetime <- as.POSIXct(hochwald.station$datetime, format = "%F %T")

hochwald.station <- hochwald.station[,names(hochwald.station) %in% c("site", "datetime", "date", "TT_TU")]

hochwald.station <- dplyr::rename(hochwald.station,
                           "station_meanair" = "TT_TU")

# There is no maximum or minimum temperature for Hochwald, but data is recorded at an hourly basis, so we will calculate daily maximum, mean and min temperatures

hochwald.dates <- seq(as.Date("2020-06-25"),as.Date("2021-01-31"), by = 'day')

hochwald.station <- hochwald.station[which(hochwald.station$date %in% hochwald.dates),]

hochwald.station.minair <- aggregate(list(station_minair = hochwald.station$station_meanair), by = list(date = hochwald.station$date), FUN = min)

hochwald.station.maxair <- aggregate(list(station_maxair = hochwald.station$station_meanair), by = list(date = hochwald.station$date), FUN = max)

hochwald.station.meanair <- aggregate(list(station_meanair = hochwald.station$station_meanair), by = list(date = hochwald.station$date), FUN = mean)

# Merge all:

hochwald.station <- merge_recurse(list(hochwald.station.minair, hochwald.station.maxair, hochwald.station.meanair))

rm(hochwald.station.maxair)
rm(hochwald.station.meanair)
rm(hochwald.station.minair)

hochwald.station$site <- "Hochwald"

rm(hochwald.dates)

# VIVARP

vivarp.station$datetime <- paste(vivarp.station$Datum, " ", vivarp.station$Tid)

vivarp.station$datetime <- as.POSIXct(vivarp.station$datetime, format = "%F %T")

vivarp.station <- vivarp.station[,names(vivarp.station) %in% c("datetime", "Datum", "Lufttemperatur")]

vivarp.station <- dplyr::rename(vivarp.station,
                         "station_meanair" = "Lufttemperatur",
                         "date" = "Datum")

vivarp.station$site <- "Vivarp"

vivarp.dates <- c(seq(as.Date("2020-12-25"),as.Date("2021-01-31"), by = 'day'), seq(as.Date("2021-06-25"),as.Date("2021-07-31"), by = 'day'))

vivarp.station$date <- as.Date(vivarp.station$date)

vivarp.station <- vivarp.station[which(vivarp.station$date %in% vivarp.dates),]

# Calculate daily maximum and minimum temperature from hourly data

vivarp.station.hourly <- vivarp.station # backup of daily data for future graphs

vivarp.station.minair <- aggregate(list(station_minair = vivarp.station$station_meanair), by = list(date = vivarp.station$date), FUN = min)

vivarp.station.maxair <- aggregate(list(station_maxair = vivarp.station$station_meanair), by = list(date = vivarp.station$date), FUN = max)

vivarp.station.meanair <- aggregate(list(station_meanair = vivarp.station$station_meanair), by = list(date = vivarp.station$date), FUN = mean)

vivarp.station <- merge_recurse(list(vivarp.station.minair, vivarp.station.maxair, vivarp.station.meanair))

rm(vivarp.station.maxair)
rm(vivarp.station.meanair)
rm(vivarp.station.minair)

vivarp.station$site <- "Vivarp"

rm(vivarp.dates)

# SILJAN

siljan.station <- siljan.station[,which(names(siljan.station) %in% c("Datum", "air_meantemp", "air_maxtemp", "air_mintemp", "site"))]

siljan.station <- rename(siljan.station,
                         "date" = "Datum",
                         "station_meanair" = "air_meantemp",
                         "station_minair" = "air_mintemp",
                         "station_maxair" = "air_maxtemp")

siljan.station$site <- "Siljan"

siljan.dates <- seq(as.Date("2020-06-25"),as.Date("2021-01-31"), by = 'day')

siljan.station$date <- as.Date(siljan.station$date)

siljan.station <- siljan.station[which(siljan.station$date %in% siljan.dates),]

rm(siljan.dates)

# SANDSJÖ

sandsjo.station <- sandsjo.station[,which(names(sandsjo.station) %in% c("Datum", "air_meantemp", "air_maxtemp", "air_mintemp", "site"))]

sandsjo.station <- rename(sandsjo.station,
                         "date" = "Datum",
                         "station_meanair" = "air_meantemp",
                         "station_minair" = "air_mintemp",
                         "station_maxair" = "air_maxtemp")

sandsjo.station$site <- "Sandsjo"

sandsjo.dates <- c(seq(as.Date("2019-12-26"),as.Date("2020-01-31"), by = 'day'), seq(as.Date("2020-06-25"),as.Date("2020-07-31"), by = 'day'))

sandsjo.station$date <- as.Date(sandsjo.station$date)

sandsjo.station <- sandsjo.station[which(sandsjo.station$date %in% sandsjo.dates),]

rm(sandsjo.dates)
```

Merge all weather station data:

```{r}
weather.stations <- rbind(arville.station, hochwald.station, vivarp.station, siljan.station, sandsjo.station)
```

Calculate rolling mean temperature for the previous five days. No precipitation this time:

```{r}
weather.stations <- weather.stations %>%
    dplyr::arrange(date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(ws_prev_av_temp = lag(zoo::rollmean(station_meanair, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>%
  dplyr::ungroup()
```

Save dataset:

```{r}
# rename "date" to "Date" for consistency
weather.stations <- dplyr::rename(weather.stations,
                              "Date" = "date")
# save
write.csv(weather.stations, file = "./DATASETS/weatherstations_merged.csv", quote = FALSE, row.names = FALSE)

rm(list = ls())
```
