# Macro vs. Microclimate

First, we need to load ERA5 data and logger data:

```{r}
logger.temp <- read.csv("./DATASETS/rawtemp_min.csv", header = TRUE)

ERA5.temp <- read.csv("./DATASETS/ERA5_raw_hour.csv", header = TRUE)
```

We will also load temperature data from local weather stations to see how much does ERA5 and our microclimate data differ from these:

```{r}
station.hochwald <- read.table("./DATASETS/Hochwald_station.txt", sep = ";", header = TRUE)
```


... and some packages:

```{r}
library(lubridate)
library(dplyr)
library(ggplot2)
```

Logger data is at a 15-min resolution, but ERA5 data is at an hourly resolution. Let's downscale logger data to 1-hour.

```{r}
logger.temp$datetime <- paste(logger.temp$Date, logger.temp$time)

logger.temp$datetime <- as.POSIXct(logger.temp$datetime, format = "%F %T")

logger.temp$hour <- hour(logger.temp$datetime)

logger.temp.2 <- logger.temp %>%
  group_by(site, Plot, location, Date, hour) %>%
  summarise(
loggertemp = (mean(Temp)))

logger.temp.2$datetime <- paste(logger.temp.2$Date, paste(logger.temp.2$hour,":00:00", sep = ""))

logger.temp.2$datetime <- as.POSIXct(logger.temp.2$datetime, format = "%F %T")
```

Merge all datasets:
```{r}
# ERA5 and microclimate
ERA5.temp$datetime <- paste(ERA5.temp$date, ERA5.temp$time) 

ERA5.temp$datetime <- as.POSIXct(ERA5.temp$datetime, format = "%F %T")

temp2 <- merge(logger.temp.2, ERA5.temp, by = c("site", "datetime"))

rm(logger.temp)
rm(logger.temp.2)
rm(ERA5.temp)

# Weather stations
temp3 <- merge(temp2, station.hochwald, by = c("site", "datetime"), all.x = TRUE)

rm(temp2)
rm(station.hochwald)

# mcera5
mcera5 <- read.csv("./DATASETS/mcera5.csv", header = TRUE)

mcera5$datetime <- as.POSIXct(mcera5$datetime, format = "%F %T")

temp <- merge(temp3, mcera5, by = c("site", "datetime"), all.x = TRUE)

# OJO!, QUE ELS VALORS DE TEMPERATURA D'AIRE D'AQUESTES DATABASES POTSER S'HAN COPIAT ALS VALORS DE TEMPERATURA DEL SOIL!!!
```


Figure:

```{r}
arville <- temp[which(temp$site == "Arville"),]

onecoldweek <- seq(as.POSIXct('2021-1-3 00:00:00'),as.POSIXct('2021-1-10 00:00:00'), by = '1 hour')

arville.week.cold <- arville[arville$datetime %in% onecoldweek,]

arville.coldplot <- ggplot(arville.week.cold[which(arville.week.cold$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 5),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 12),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 34),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 38),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 40),]$loggertemp)) + 
  geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
   ggtitle("Arville coldest month")
  
#rm(arville.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(as.POSIXct('2020-7-1 00:00:00'),as.POSIXct('2020-7-8 00:00:00'), by = '1 hour')

arville.week.warm <- arville[arville$datetime %in% onewarmweek,]

arville.warmplot <- 
  ggplot(arville.week.warm[which(arville.week.warm$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 5),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 12),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 34),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 38),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 40),]$loggertemp)) + 
  geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
   ggtitle("Arville warmest month")
  
rm(arville)
#rm(arville.week.warm)
```

Hochwald:

```{r}
hochwald <- temp[which(temp$site == "Hochwald"),]

hochwald <- hochwald[which(hochwald$location == "a"),]

onecoldweek <- seq(as.POSIXct('2021-1-3 00:00:00'),as.POSIXct('2021-1-10 00:00:00'), by = '1 hour')

hochwald.week.cold <- hochwald[hochwald$datetime %in% onecoldweek,]


hochwald.coldplot <- 
  ggplot(hochwald.week.cold[which(hochwald.week.cold$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 5),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 12),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 33),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 38),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 40),]$loggertemp)) + 
  geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = maxair_mcera5), colour = "dark red", lwd = 2) +
    geom_line(aes(y = minair_mcera5), colour = "orange", lwd = 2) +
    geom_line(aes(y = hochwald_station_air), colour = "green", lwd = 2) +
      geom_line(aes(y = mcera5_airtemp), colour = "purple", lwd = 2) +
  ggtitle("Hochwald coldest month")
  
#rm(hochwald.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(as.POSIXct('2020-7-1 00:00:00'),as.POSIXct('2020-7-8 00:00:00'), by = '1 hour')

hochwald.week.warm <- hochwald[hochwald$datetime %in% onewarmweek,]

hochwald.warmplot <- 
  ggplot(hochwald.week.warm[which(hochwald.week.warm$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 5),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 12),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 33),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 38),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 40),]$loggertemp)) + 
  geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = maxair_mcera5), colour = "dark red", lwd = 2) +
    geom_line(aes(y = minair_mcera5), colour = "orange", lwd = 2) +
    geom_line(aes(y = hochwald_station_air), colour = "green", lwd = 2) +      
  geom_line(aes(y = mcera5_airtemp), colour = "purple", lwd = 2) +
  ggtitle("Hochwald warmest month")

rm(hochwald)
#rm(hochwald.week.warm)
```

Vivarp:

```{r}
vivarp <- temp[which(temp$site == "Vivarp"),]

vivarp <- vivarp[which(vivarp$location == "a"),]

onecoldweek <- seq(as.POSIXct('2021-1-3 00:00:00'),as.POSIXct('2021-1-10 00:00:00'), by = '1 hour')

vivarp.week.cold <- vivarp[vivarp$datetime %in% onecoldweek,]

vivarp.coldplot <- ggplot(vivarp.week.cold[which(vivarp.week.cold$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 12),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 34),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Vivarp coldest month")
  
#rm(vivarp.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(as.POSIXct('2021-7-1 00:00:00'),as.POSIXct('2021-7-8 00:00:00'), by = '1 hour')

vivarp.week.warm <- vivarp[vivarp$datetime %in% onewarmweek,]

vivarp.warmplot <- 
  ggplot(vivarp.week.warm[which(vivarp.week.warm$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 2),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 11),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 12),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 25),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 27),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 28),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 31),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 34),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Vivarp warmest month")

rm(vivarp)
#rm(vivarp.week.warm)
```

Siljan:

```{r}
siljan <- temp[which(temp$site == "Siljan"),]

siljan <- siljan[which(siljan$location == "a"),]

onecoldweek <- seq(as.POSIXct('2021-1-3 00:00:00'),as.POSIXct('2021-1-10 00:00:00'), by = '1 hour')

siljan.week.cold <- siljan[siljan$datetime %in% onecoldweek,]

siljan.coldplot <- 
  ggplot(siljan.week.cold[which(siljan.week.cold$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 11),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 34),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Siljan coldest month")
  
#rm(siljan.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(as.POSIXct('2020-7-1 00:00:00'),as.POSIXct('2020-7-8 00:00:00'), by = '1 hour')

siljan.week.warm <- siljan[siljan$datetime %in% onewarmweek,]

siljan.warmplot <- 
  ggplot(siljan.week.warm[which(siljan.week.warm$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 2),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 11),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 17),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 20),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 25),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 27),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 28),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 29),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 31),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 34),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 37),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Hochwald warmest month")

rm(siljan)
#rm(siljan.week.warm)
```

Sandsjö:

```{r}
sandsjo <- temp[which(temp$site == "Sandsjo"),]

sandsjo <- sandsjo[which(sandsjo$location == "a"),]

onecoldweek <- seq(as.POSIXct('2020-1-1 00:00:00'),as.POSIXct('2020-1-8 00:00:00'), by = '1 hour')

sandsjo.week.cold <- sandsjo[sandsjo$datetime %in% onecoldweek,]

sandsjo.coldplot <- 
  ggplot(sandsjo.week.cold[which(sandsjo.week.cold$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 2),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 11),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 12),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 13),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 17),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 19),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 25),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 27),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 28),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 29),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 31),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 34),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Sandsjö coldest month")

#rm(sandsjo.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(as.POSIXct('2020-7-1 00:00:00'),as.POSIXct('2020-7-8 00:00:00'), by = '1 hour')

sandsjo.week.warm <- sandsjo[sandsjo$datetime %in% onewarmweek,]

sandsjo.warmplot <- 
  ggplot(sandsjo.week.warm[which(sandsjo.week.warm$Plot == 1),], aes(x = datetime)) +
geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 1),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 2),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 3),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 4),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 5),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 6),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 7),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 8),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 9),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 10),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 11),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 12),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 13),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 14),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 15),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 16),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 17),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 18),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 19),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 21),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 22),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 23),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 24),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 25),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 26),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 27),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 28),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 29),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 30),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 31),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 32),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 33),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 34),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 35),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 36),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 38),]$loggertemp)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 39),]$loggertemp)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 40),]$loggertemp)) + 
      geom_line(aes(y = air_meantemp), colour = "red", lwd = 2) +
    geom_line(aes(y = air_maxtemp), colour = "dark red", lwd = 2) +
    geom_line(aes(y = air_mintemp), colour = "orange", lwd = 2) +
  ggtitle("Sandsjö warmest month")

rm(sandsjo)
#rm(sandsjo.week.warm)

rm(onecoldweek)
rm(onewarmweek)

#rm(temp)
```


```{r}
library(gridExtra)

grid.arrange(arville.coldplot,
arville.warmplot,
hochwald.coldplot,
hochwald.warmplot,
vivarp.coldplot,
vivarp.warmplot,
siljan.coldplot,
siljan.warmplot,
sandsjo.coldplot,
sandsjo.warmplot, ncol=2)
```