# Offeset calculation and dataset merging

First, we need to load ERA5 data and logger data:

```{r}
logger.temp <- read.csv("./DATASETS/logger_temp.csv", header = TRUE)

ERA5.temp <- read.csv("./DATASETS/ERA5_temp.csv", header = TRUE)
```

###############
Calculate mean temperature and precipitation for the five previous days

```{r}
library(dplyr)
library(zoo)

ERA5.temp <- ERA5.temp %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(prev_av_temp = lag(zoo::rollmean(era5_air, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>% 
  dplyr::ungroup()

ERA5.temp <- ERA5.temp %>%
    dplyr::arrange(Date) %>% 
    dplyr::arrange(desc(site)) %>% 
    dplyr::group_by(site) %>% 
    dplyr::mutate(prev_av_prec = lag(zoo::rollmean(prec, 
                                               k = 5, 
                                               fill = NA), n = 3)) %>% 
  dplyr::ungroup()
```

###############


And we merge them by site and date:

```{r}
temp <- merge(logger.temp, ERA5.temp, by = c("site", "Date"))

rm(logger.temp)
rm(ERA5.temp)
```

Calculate temperature offsets:

```{r}
temp$air_off <- temp$Temp.mean - temp$era5_air # air mean temperature

temp[which(temp$location == "s"),]$air_off <- NA # knock out values for soil loggers, as this will be calculated with "era5_soil"

temp$min_off <- temp$Temp.min - temp$era5_min

temp[which(temp$location == "s"),]$min_off <- NA # remove minimum values for soil temperature, as offsets are calculated with minimum air temperature.

temp$max_off <- temp$Temp.max - temp$era5_max

temp[which(temp$location == "s"),]$max_off <- NA # remove maximum values for soil temperature, as offsets are calculated with minimum air

temp$soil_off <- temp$Temp.mean-temp$era5_soil

temp[which(temp$location == "a"),]$soil_off <- NA # remove values obtained for air loggers, as offsets have been calculated with soil temperature
```

# Merge with tree data

Load tree data:

```{r}
tree.data <- read.csv("./DATASETS/tree_data.csv", header = TRUE)
```

Merge the temperature dataset and the tree data:

```{r}
tree.temp <- merge(temp, tree.data, by = c("site", "Plot"))

rm(temp)
rm(tree.data)
```

Export the merged dataset:

```{r}
write.csv(tree.temp, file = "./DATASETS/tree_temp.csv", row.names = FALSE, quote = FALSE)

#rm(list = ls())
```

Figure:

```{r}
arville <- tree.temp[which(tree.temp$site == "Arville"),]

library(lubridate)

onecoldweek <- seq(ymd('2021-1-1'),ymd('2021-1-31'), by = '1 d')
arville$Date <- as.Date(arville$Date)

arville.week.cold <- arville[arville$Date %in% onecoldweek,]

macroclimate.arville.cold.meanair <- aggregate(arville.week.cold$era5_air, by = list(arville.week.cold$Date), FUN = mean)

macroclimate.arville.cold.maxair <- aggregate(arville.week.cold$era5_max, by = list(arville.week.cold$Date), FUN = max)

macroclimate.arville.cold.minair <- aggregate(arville.week.cold$era5_min, by = list(arville.week.cold$Date), FUN = min)

macroclimate.arville.cold.meansoil <- aggregate(arville.week.cold$era5_soil, by = list(arville.week.cold$Date), FUN = mean)

macroclimate.arville.cold <- cbind(macroclimate.arville.cold.meanair, macroclimate.arville.cold.maxair, macroclimate.arville.cold.minair, macroclimate.arville.cold.meansoil)

macroclimate.arville.cold <- macroclimate.arville.cold[,c(1,2,4,6, 8)]

names(macroclimate.arville.cold) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")

library(ggplot2)
arville.coldplot <- ggplot(macroclimate.arville.cold, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 5),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 12),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 34),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 38),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.cold[which(arville.week.cold$Plot == 40),]$Temp.mean)) + 
  geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
   ggtitle("Arville coldest month")
  
#rm(macroclimate.arville.cold)
#rm(arville.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(ymd('2020-7-1'),ymd('2020-7-31'), by = '1 d')

arville.week.warm <- arville[arville$Date %in% onewarmweek,]

macroclimate.arville.warm.meanair <- aggregate(arville.week.warm$era5_air, by = list(arville.week.warm$Date), FUN = mean)

macroclimate.arville.warm.maxair <- aggregate(arville.week.warm$era5_max, by = list(arville.week.warm$Date), FUN = max)

macroclimate.arville.warm.minair <- aggregate(arville.week.warm$era5_min, by = list(arville.week.warm$Date), FUN = min)

macroclimate.arville.warm.meansoil <- aggregate(arville.week.warm$era5_soil, by = list(arville.week.warm$Date), FUN = mean)

macroclimate.arville.warm <- cbind(macroclimate.arville.warm.meanair, macroclimate.arville.warm.maxair, macroclimate.arville.warm.minair, macroclimate.arville.warm.meansoil)

macroclimate.arville.warm <- macroclimate.arville.warm[,c(1,2,4,6, 8)]

names(macroclimate.arville.warm) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")

arville.warmplot <- ggplot(macroclimate.arville.warm, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 5),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 12),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 34),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 38),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= arville.week.warm[which(arville.week.warm$Plot == 40),]$Temp.mean)) + 
  geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Arville warmest month")

rm(arville)
#rm(arville.week.warm)
#rm(macroclimate.arville.warm)
```

Hochwald:

```{r}
hochwald <- tree.temp[which(tree.temp$site == "Hochwald"),]

hochwald <- hochwald[which(hochwald$location == "a"),]

onecoldweek <- seq(ymd('2021-1-1'),ymd('2021-1-31'), by = '1 d')
hochwald$Date <- as.Date(hochwald$Date)

hochwald.week.cold <- hochwald[hochwald$Date %in% onecoldweek,]

macroclimate.hochwald.cold.meanair <- aggregate(hochwald.week.cold$era5_air, by = list(hochwald.week.cold$Date), FUN = mean)

macroclimate.hochwald.cold.maxair <- aggregate(hochwald.week.cold$era5_max, by = list(hochwald.week.cold$Date), FUN = max)

macroclimate.hochwald.cold.minair <- aggregate(hochwald.week.cold$era5_min, by = list(hochwald.week.cold$Date), FUN = min)

macroclimate.hochwald.cold.meansoil <- aggregate(hochwald.week.cold$era5_soil, by = list(hochwald.week.cold$Date), FUN = mean)

macroclimate.hochwald.cold <- cbind(macroclimate.hochwald.cold.meanair, macroclimate.hochwald.cold.maxair, macroclimate.hochwald.cold.minair, macroclimate.hochwald.cold.meansoil)

macroclimate.hochwald.cold <- macroclimate.hochwald.cold[,c(1,2,4,6, 8)]

names(macroclimate.hochwald.cold) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


hochwald.coldplot <- ggplot(macroclimate.hochwald.cold, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 5),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 12),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 33),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 38),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.cold[which(hochwald.week.cold$Plot == 40),]$Temp.mean)) + 
  geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Hochwald coldest month")
  
#rm(macroclimate.hochwald.cold)
#rm(hochwald.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(ymd('2020-7-1'),ymd('2020-7-31'), by = '1 d')

hochwald.week.warm <- hochwald[hochwald$Date %in% onewarmweek,]

macroclimate.hochwald.warm.meanair <- aggregate(hochwald.week.warm$era5_air, by = list(hochwald.week.warm$Date), FUN = mean)

macroclimate.hochwald.warm.maxair <- aggregate(hochwald.week.warm$era5_max, by = list(hochwald.week.warm$Date), FUN = max)

macroclimate.hochwald.warm.minair <- aggregate(hochwald.week.warm$era5_min, by = list(hochwald.week.warm$Date), FUN = min)

macroclimate.hochwald.warm.meansoil <- aggregate(hochwald.week.warm$era5_soil, by = list(hochwald.week.warm$Date), FUN = mean)

macroclimate.hochwald.warm <- cbind(macroclimate.hochwald.warm.meanair, macroclimate.hochwald.warm.maxair, macroclimate.hochwald.warm.minair, macroclimate.hochwald.warm.meansoil)

macroclimate.hochwald.warm <- macroclimate.hochwald.warm[,c(1,2,4,6, 8)]

names(macroclimate.hochwald.warm) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


hochwald.warmplot <- ggplot(macroclimate.hochwald.warm, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 5),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 12),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 27),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 26),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 31),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 38),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= hochwald.week.warm[which(hochwald.week.warm$Plot == 40),]$Temp.mean)) + 
  geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Hochwald warmest month")

rm(hochwald)
#rm(hochwald.week.warm)
#rm(macroclimate.hochwald.warm)
```

Vivarp:

```{r}
vivarp <- tree.temp[which(tree.temp$site == "Vivarp"),]

vivarp <- vivarp[which(vivarp$location == "a"),]

onecoldweek <- seq(ymd('2021-1-1'),ymd('2021-1-31'), by = '1 d')
vivarp$Date <- as.Date(vivarp$Date)

vivarp.week.cold <- vivarp[vivarp$Date %in% onecoldweek,]

macroclimate.vivarp.cold.meanair <- aggregate(vivarp.week.cold$era5_air, by = list(vivarp.week.cold$Date), FUN = mean)

macroclimate.vivarp.cold.maxair <- aggregate(vivarp.week.cold$era5_max, by = list(vivarp.week.cold$Date), FUN = max)

macroclimate.vivarp.cold.minair <- aggregate(vivarp.week.cold$era5_min, by = list(vivarp.week.cold$Date), FUN = min)

macroclimate.vivarp.cold.meansoil <- aggregate(vivarp.week.cold$era5_soil, by = list(vivarp.week.cold$Date), FUN = mean)

macroclimate.vivarp.cold <- cbind(macroclimate.vivarp.cold.meanair, macroclimate.vivarp.cold.maxair, macroclimate.vivarp.cold.minair, macroclimate.vivarp.cold.meansoil)

macroclimate.vivarp.cold <- macroclimate.vivarp.cold[,c(1,2,4,6, 8)]

names(macroclimate.vivarp.cold) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


vivarp.coldplot <- ggplot(macroclimate.vivarp.cold, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 12),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 34),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.cold[which(vivarp.week.cold$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Vivarp coldest month")
  
#rm(macroclimate.vivarp.cold)
#rm(vivarp.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(ymd('2021-7-1'),ymd('2021-7-31'), by = '1 d')

vivarp.week.warm <- vivarp[vivarp$Date %in% onewarmweek,]

macroclimate.vivarp.warm.meanair <- aggregate(vivarp.week.warm$era5_air, by = list(vivarp.week.warm$Date), FUN = mean)

macroclimate.vivarp.warm.maxair <- aggregate(vivarp.week.warm$era5_max, by = list(vivarp.week.warm$Date), FUN = max)

macroclimate.vivarp.warm.minair <- aggregate(vivarp.week.warm$era5_min, by = list(vivarp.week.warm$Date), FUN = min)

macroclimate.vivarp.warm.meansoil <- aggregate(vivarp.week.warm$era5_soil, by = list(vivarp.week.warm$Date), FUN = mean)

macroclimate.vivarp.warm <- cbind(macroclimate.vivarp.warm.meanair, macroclimate.vivarp.warm.maxair, macroclimate.vivarp.warm.minair, macroclimate.vivarp.warm.meansoil)

macroclimate.vivarp.warm <- macroclimate.vivarp.warm[,c(1,2,4,6, 8)]

names(macroclimate.vivarp.warm) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


vivarp.warmplot <- ggplot(macroclimate.vivarp.warm, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 2),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 11),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 12),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 25),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 27),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 28),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 31),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 34),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= vivarp.week.warm[which(vivarp.week.warm$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Vivarp warmest month")

rm(vivarp)
#rm(vivarp.week.warm)
#rm(macroclimate.vivarp.warm)
```

Siljan:

```{r}
siljan <- tree.temp[which(tree.temp$site == "Siljan"),]

siljan <- siljan[which(siljan$location == "a"),]

onecoldweek <- seq(ymd('2021-1-1'),ymd('2021-1-31'), by = '1 d')
siljan$Date <- as.Date(siljan$Date)

siljan.week.cold <- siljan[siljan$Date %in% onecoldweek,]

macroclimate.siljan.cold.meanair <- aggregate(siljan.week.cold$era5_air, by = list(siljan.week.cold$Date), FUN = mean)

macroclimate.siljan.cold.maxair <- aggregate(siljan.week.cold$era5_max, by = list(siljan.week.cold$Date), FUN = max)

macroclimate.siljan.cold.minair <- aggregate(siljan.week.cold$era5_min, by = list(siljan.week.cold$Date), FUN = min)

macroclimate.siljan.cold.meansoil <- aggregate(siljan.week.cold$era5_soil, by = list(siljan.week.cold$Date), FUN = mean)

macroclimate.siljan.cold <- cbind(macroclimate.siljan.cold.meanair, macroclimate.siljan.cold.maxair, macroclimate.siljan.cold.minair, macroclimate.siljan.cold.meansoil)

macroclimate.siljan.cold <- macroclimate.siljan.cold[,c(1,2,4,6, 8)]

names(macroclimate.siljan.cold) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")

siljan.coldplot <- ggplot(macroclimate.siljan.cold, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 11),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 34),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.cold[which(siljan.week.cold$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Siljan coldest month")
  
#rm(macroclimate.siljan.cold)
#rm(siljan.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(ymd('2020-7-1'),ymd('2020-7-31'), by = '1 d')

siljan.week.warm <- siljan[siljan$Date %in% onewarmweek,]

macroclimate.siljan.warm.meanair <- aggregate(siljan.week.warm$era5_air, by = list(siljan.week.warm$Date), FUN = mean)

macroclimate.siljan.warm.maxair <- aggregate(siljan.week.warm$era5_max, by = list(siljan.week.warm$Date), FUN = max)

macroclimate.siljan.warm.minair <- aggregate(siljan.week.warm$era5_min, by = list(siljan.week.warm$Date), FUN = min)

macroclimate.siljan.warm.meansoil <- aggregate(siljan.week.warm$era5_soil, by = list(siljan.week.warm$Date), FUN = mean)

macroclimate.siljan.warm <- cbind(macroclimate.siljan.warm.meanair, macroclimate.siljan.warm.maxair, macroclimate.siljan.warm.minair, macroclimate.siljan.warm.meansoil)

macroclimate.siljan.warm <- macroclimate.siljan.warm[,c(1,2,4,6, 8)]

names(macroclimate.siljan.warm) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


siljan.warmplot <- ggplot(macroclimate.siljan.warm, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 2),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 11),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 17),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 20),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 25),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 27),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 28),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 29),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 31),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 34),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 37),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= siljan.week.warm[which(siljan.week.warm$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Hochwald warmest month")

rm(siljan)
#rm(siljan.week.warm)
#rm(macroclimate.siljan.warm)
```

Sandsj:

```{r}
sandsjo <- tree.temp[which(tree.temp$site == "Sandsjo"),]

sandsjo <- sandsjo[which(sandsjo$location == "a"),]

onecoldweek <- seq(ymd('2020-1-1'),ymd('2020-1-31'), by = '1 d')
sandsjo$Date <- as.Date(sandsjo$Date)

sandsjo.week.cold <- sandsjo[sandsjo$Date %in% onecoldweek,]

macroclimate.sandsjo.cold.meanair <- aggregate(sandsjo.week.cold$era5_air, by = list(sandsjo.week.cold$Date), FUN = mean)

macroclimate.sandsjo.cold.maxair <- aggregate(sandsjo.week.cold$era5_max, by = list(sandsjo.week.cold$Date), FUN = max)

macroclimate.sandsjo.cold.minair <- aggregate(sandsjo.week.cold$era5_min, by = list(sandsjo.week.cold$Date), FUN = min)

macroclimate.sandsjo.cold.meansoil <- aggregate(sandsjo.week.cold$era5_soil, by = list(sandsjo.week.cold$Date), FUN = mean)

macroclimate.sandsjo.cold <- cbind(macroclimate.sandsjo.cold.meanair, macroclimate.sandsjo.cold.maxair, macroclimate.sandsjo.cold.minair, macroclimate.sandsjo.cold.meansoil)

macroclimate.sandsjo.cold <- macroclimate.sandsjo.cold[,c(1,2,4,6, 8)]

names(macroclimate.sandsjo.cold) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


sandsjo.coldplot <- ggplot(macroclimate.sandsjo.cold, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 2),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 11),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 12),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 13),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 17),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 19),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 25),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 27),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 28),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 29),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 31),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 34),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.cold[which(sandsjo.week.cold$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Sandsj coldest month")

#rm(macroclimate.sandsjo.cold)
#rm(sandsjo.week.cold)

# Same with warmest month (july):

onewarmweek <- seq(ymd('2020-7-1'),ymd('2020-7-31'), by = '1 d')

sandsjo.week.warm <- sandsjo[sandsjo$Date %in% onewarmweek,]

macroclimate.sandsjo.warm.meanair <- aggregate(sandsjo.week.warm$era5_air, by = list(sandsjo.week.warm$Date), FUN = mean)

macroclimate.sandsjo.warm.maxair <- aggregate(sandsjo.week.warm$era5_max, by = list(sandsjo.week.warm$Date), FUN = max)

macroclimate.sandsjo.warm.minair <- aggregate(sandsjo.week.warm$era5_min, by = list(sandsjo.week.warm$Date), FUN = min)

macroclimate.sandsjo.warm.meansoil <- aggregate(sandsjo.week.warm$era5_soil, by = list(sandsjo.week.warm$Date), FUN = mean)

macroclimate.sandsjo.warm <- cbind(macroclimate.sandsjo.warm.meanair, macroclimate.sandsjo.warm.maxair, macroclimate.sandsjo.warm.minair, macroclimate.sandsjo.warm.meansoil)

macroclimate.sandsjo.warm <- macroclimate.sandsjo.warm[,c(1,2,4,6, 8)]

names(macroclimate.sandsjo.warm) <- c("Date", "mean_era5_air", "max_era5_air", "min_era5_air", "mean_era5_soil")


sandsjo.warmplot <- ggplot(macroclimate.sandsjo.warm, aes(x = Date)) +
geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 1),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 2),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 3),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 4),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 5),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 6),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 7),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 8),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 9),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 10),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 11),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 12),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 13),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 14),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 15),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 16),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 17),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 18),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 19),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 21),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 22),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 23),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 24),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 25),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 26),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 27),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 28),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 29),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 30),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 31),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 32),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 33),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 34),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 35),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 36),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 38),]$Temp.mean)) +
    geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 39),]$Temp.mean)) +
  geom_line(color = "gray45", alpha = 0.5, lwd = 1, aes(y= sandsjo.week.warm[which(sandsjo.week.warm$Plot == 40),]$Temp.mean)) + 
      geom_line(aes(y = mean_era5_air), colour = "red", lwd = 2) +
    geom_line(aes(y = max_era5_air), colour = "dark red", lwd = 2) +
    geom_line(aes(y = min_era5_air), colour = "orange", lwd = 2) +
  ggtitle("Sandsj warmest month")

rm(sandsjo)
#rm(sandsjo.week.warm)
#rm(macroclimate.sandsjo.warm)

rm(onecoldweek)
rm(onewarmweek)

rm(tree.temp)
```


```{r}
library(gridExtra)

grid.arrange(arville.coldplot,
arville.warmplot,
hochwald.coldplot,
hochwald.warmplot,
vivarp.coldplot,
vivarp.warmplot,
siljan.coldplot,
siljan.warmplot,
sandsjo.coldplot,
sandsjo.warmplot, ncol=2)
```

