---
title: "Basal area script"
author: "Joan Diaz Calafat"
date: "6/7/2021"
output: html_document
---

Load data:

```{r}
trees <- read.csv("Träddata_Vindeln_Complete.csv", header = TRUE, sep = ";", dec = ",")
```

We only consider as trees anything above 5cm DBH:

```{r}
trees <- trees[which(trees$DBH >= 5),]
```

Calculate "real distances" to the center of the plot:
_DBH is in mm, distance is in m._
```{r}
trees$real.dist <- trees$Distance + (trees$DBH/2)/1000
```

Group by site and plot number and calculate basal area for different distance intervals to the center of the plot (i.e. to the temeprature logger):

```{r}
library(dplyr)

trees <- trees %>%
  filter(real.dist <= 10) %>%
  group_by(Site, Plot) %>%
  summarise(Basal_Area_10m = (sum(pi*(((DBH[real.dist <= 10]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_9m = (sum(pi*(((DBH[real.dist <= 9]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_8m = (sum(pi*(((DBH[real.dist <= 8]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_7m = (sum(pi*(((DBH[real.dist <= 7]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_6m = (sum(pi*(((DBH[real.dist <= 6]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_5m = (sum(pi*(((DBH[real.dist <= 5]/2)/1000))^2)/((pi*10^2))*10000),
Basal_Area_4m = (sum(pi*(((DBH[real.dist <= 4]/2)/1000))^2)/((pi*10^2))*10000))
```

Load temperature data and calculate mean, min and max temperatures for both soil and air loggers:

```{r}
# From tree data to basal area
setwd("J:/TEMPERATURE DATA/SILJAN/202103_SILJAN_TEMPERATURE/")

file.list <- list.files(path = ".", pattern = "*.xlsx", all.files = FALSE,
                        full.names = FALSE, recursive = FALSE,
                        ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

library(readxl)

# Load data without skipping rows and setting column names:
df.list <- lapply(file.list, read_excel)

data.temp <- do.call(rbind, df.list)
```

Data completeness:

```{r}
library(lubridate)
oneyear <- seq(ymd_hm('2019-10-28 18:15'),ymd_hm('2020-10-28 18:00'), by = '15 mins')
data.temp <- data.temp[which(data.temp$Date_time %in% oneyear),]

temp.air <- data.temp[which(data.temp$location == "a"),]
temp.soil <- data.temp[which(data.temp$location == "s"),]

library(reshape2)
dates.air.plot <- dcast(temp.air, Date_time ~ Plot)
# soil
dates.soil.plot <- dcast(temp.soil, Date_time ~ Plot)
library(naniar)
# air
vis_miss(dates.air.plot, warn_large_data = FALSE)
# soil
vis_miss(dates.soil.plot, warn_large_data = FALSE)
```

Let's split date and time into different variables:

```{r}
library(stringr)
temp  <- cbind(str_split_fixed(data.temp$Date_time, " ", length(colnames(data.temp)) +1), data.temp[,-3])
colnames(temp) <- c("Date", "Time", "Day", "Month", "Year", "Plot", "Location", "Temp")
library(lubridate)
temp$Day <- day(temp$Date)
temp$Month <- month(temp$Date)
temp$Year <- year(temp$Date)

# We separate air and soil data again:

temp.air <- temp[which(temp$Location == "a"),]
temp.soil <- temp[which(temp$Location == "s"),]
```

Calculate mean, max and min temperatures for each air and soil logger in each plot:

```{r}
# MEAN
av.temp.a <- aggregate(temp.air$Temp~temp.air$Plot, FUN = mean)
colnames(av.temp.a) <- c("Plot", "Mean_Temp")
av.temp.s <- aggregate(temp.soil$Temp, by = list(temp.soil$Plot), FUN = mean)
colnames(av.temp.s) <- c("Plot", "Mean_Temp")

# MAX
max.temp.a <- aggregate(temp.air$Temp~temp.air$Plot, FUN = max)
colnames(max.temp.a) <- c("Plot", "Max_Temp")
max.temp.s <- aggregate(temp.soil$Temp, by = list(temp.soil$Plot), FUN = max)
colnames(max.temp.s) <- c("Plot", "Max_Temp")

# MIN
min.temp.a <- aggregate(temp.air$Temp~temp.air$Plot, FUN = min)
colnames(min.temp.a) <- c("Plot", "Min_Temp")
min.temp.s <- aggregate(temp.soil$Temp, by = list(temp.soil$Plot), FUN = min)
colnames(min.temp.s) <- c("Plot", "Min_Temp")
```

Merge all air and all soil temperatures into different objects:

```{r}
data.temp.a <- cbind(av.temp.a, min.temp.a, max.temp.a)
data.temp.a <- data.temp.a[,c(1,2,4,6)]
data.temp.s <- cbind(av.temp.s, min.temp.s, max.temp.s)
data.temp.s <- data.temp.s[,c(1,2,4,6)]
```

Merge tree and temperature data:

```{r}
siljan.treetemp.a <- merge(trees, data.temp.a, by = "Plot")
# Problematic plots?
siljan.treetemp.a <- siljan.treetemp.a[-which(siljan.treetemp.a$Plot == 12),] 
siljan.treetemp.a <- siljan.treetemp.a[-which(siljan.treetemp.a$Plot == 14),] 
siljan.treetemp.a <- siljan.treetemp.a[-which(siljan.treetemp.a$Plot == 21),] 
siljan.treetemp.a <- siljan.treetemp.a[-which(siljan.treetemp.a$Plot == 30),] 

siljan.treetemp.s <- merge(trees, data.temp.s, by = "Plot")
# Problematic plots?
siljan.treetemp.s <- siljan.treetemp.s[-which(siljan.treetemp.s$Plot == 2),] 
siljan.treetemp.s <- siljan.treetemp.s[-which(siljan.treetemp.s$Plot == 13),] 
siljan.treetemp.s <- siljan.treetemp.s[-which(siljan.treetemp.s$Plot == 33),] 
```

Visualize correlations between temperature and basal area at different distances from the temperature logger:

```{r}
library(GGally)

ggpairs(siljan.treetemp.a,
        columns = 2:length(siljan.treetemp.a), # That is all variables (=columns) except the first one, but depends on your dataset
        lower=list(continuous = "smooth", combo = "facethist", discrete = "facetbar", na = "na"),
        diag=list(continuous=wrap("barDiag", color='white', fill='darkgreen')),
        upper=list(continuous=wrap("cor", method = "spearman", title='Corr', stars=T)))


ggpairs(siljan.treetemp.s,
        columns = 2:length(siljan.treetemp.a), # That is all variables (=columns) except the first one, but depends on your dataset
        lower=list(continuous = "smooth", combo = "facethist", discrete = "facetbar", na = "na"),
        diag=list(continuous=wrap("barDiag", color='white', fill='darkgreen')),
        upper=list(continuous=wrap("cor", method = "spearman", title='Corr', stars=T)))

```

